Compact Routing for Today's Internet

### 2019-04-22 dissertation/dissertation.tex
tex update
trying

\documentclass{mpaper}
\usepackage{subfigure}
\usepackage{caption}

@@

\title{Dissertation}
\author{Benas Jonynas}
\matricnum{2133815}

@@

\begin{figure*}
  \centering
  \subfigure[the growth in the number of ASes visible to BGPStream between 2001 and 2019 ]{\includegraphics[width=.4\paperwidth]{images/num-nodes-all.pdf}}\hfill
  \subfigure[the growth in the number of entries in BGP routing tables between 2001 and 2019 \cite{CIDR-Report}]{\includegraphics[width=.4\paperwidth]{images/bgpEntries.png}}
  \caption {Growth in the number of AS numbers detected using BGPStream and the number of entries in BGP routing tables}
\end{figure*}

@@

\begin{figure*}
  \centering
  \subfigure[the number of ASes discovered ]{\includegraphics[width=.4\paperwidth]{images/num-nodes.pdf}}\hfill
  \subfigure[the number of connections between ASes discovered  ]{\includegraphics[width=.4\paperwidth]{images/num_edges.pdf}}\hfill
  \caption{The difference in number of ASes and connections between them discovered when using the set of oldest collectors and all available collectors}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics{images/path-frequencies.pdf}
    \caption{Numbers of nodes with different degrees of connectivity}
    \captionsetup{justification=centering}
\end{figure*}

\begin{figure*}
  \centering
  \subfigure[the percentage of snapshots with clusters greater than 0 ]{\includegraphics[width=.4\paperwidth]{images/nodes-with-clusters.pdf}}\hfill
  \subfigure[the average cluster size of nodes that have a cluster size greater than 0 ]{\includegraphics[width=.4\paperwidth]{images/average-cluster-size.pdf}}\hfill
  \caption{Cluster data for each snapshot}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics{images/k-cores.pdf}
    \caption{The sizes of k-max, k+1, and $s$ and the total number of nodes in each snapshot}
\end{figure*}

\begin{figure*}
  \centering
  \subfigure[Average shortest path length for each year using TZ routing]{\includegraphics[width=.4\paperwidth]{images/path-averages.pdf}}\hfill
  \subfigure[the average path stretch for each snapshot using TZ routing ]{\includegraphics[width=.4\paperwidth]{images/path-stretch.pdf}}\hfill
\end{figure*}

>>>>

\documentclass{dissertation/mpaper}
\usepackage{subfigure}
\usepackage{caption}

@@

\title{Compact Routing for Today's Internet}
\author{Benas Jonynas}
\matricnum{2133815}

@@

\begin{figure*}
  \centering
  \subfigure[the growth in the number of ASes visible to BGPStream between 2001 and 2019 ]{\includegraphics[width=.4\paperwidth]{dissertation/images/num-nodes-all.pdf}}\hfill
  \subfigure[the growth in the number of entries in BGP routing tables between 2001 and 2019 \cite{CIDR-Report}]{\includegraphics[width=.4\paperwidth]{dissertation/images/bgpEntries.png}}
  \caption {Growth in the number of AS numbers detected using BGPStream and the number of entries in BGP routing tables}
\end{figure*}

@@

\begin{figure*}
  \centering
  \subfigure[the number of ASes discovered ]{\includegraphics[width=.4\paperwidth]{dissertation/images/num-nodes.pdf}}\hfill
  \subfigure[the number of connections between ASes discovered  ]{\includegraphics[width=.4\paperwidth]{dissertation/images/num_edges.pdf}}\hfill
  \caption{The difference in number of ASes and connections between them discovered when using the set of oldest collectors and all available collectors}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics{dissertation/images/path-frequencies.pdf}
    \caption{Numbers of nodes with different degrees of connectivity}
    \captionsetup{justification=centering}
\end{figure*}

\begin{figure*}
  \centering
  \subfigure[the percentage of snapshots with clusters greater than 0 ]{\includegraphics[width=.4\paperwidth]{dissertation/images/nodes-with-clusters.pdf}}\hfill
  \subfigure[the average cluster size of nodes that have a cluster size greater than 0 ]{\includegraphics[width=.4\paperwidth]{dissertation/images/average-cluster-size.pdf}}\hfill
  \caption{Cluster data for each snapshot}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics{dissertation/images/k-cores.pdf}
    \caption{The sizes of k-max, k+1, and $s$ and the total number of nodes in each snapshot}
\end{figure*}

\begin{figure*}
  \centering
  \subfigure[Average shortest path length for each year using TZ routing]{\includegraphics[width=.4\paperwidth]{dissertation/images/path-averages.pdf}}\hfill
  \subfigure[the average path stretch for each snapshot using TZ routing ]{\includegraphics[width=.4\paperwidth]{dissertation/images/path-stretch.pdf}}\hfill
\end{figure*}
